---
title: "CSCI Summary"
author: Tri C. Optera
format: html
---

## Data

Let's use the CSCI dataset and provide a couple quick summaries. First we load the libraries we need.

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(gt)
library(sf)

```

## Load the Data

```{r}
#| label: import-data
#| echo: true

# give the full URL to our data (a csv file)
csci_url <- "https://raw.githubusercontent.com/SCCWRP/CABW2018_R_training/master/data/cscidat.csv"

# read in this data and assign it to the name `cscidat`
cscidat <- read.csv(csci_url)

```


## Summaries

Next we add a figure. We can also summarize our total site count and show the distribution of CSCI scores.

```{r}
#| warning: false
#| echo: false

ggplot(data=cscidat,
       aes(y = CSCI)) +
  geom_histogram() +
  labs(y = "CSCI") +
  theme_minimal()

```
There are `r cscidat |> distinct(StationCode, .keep_all = TRUE) |> nrow()` unique stations in this dataset.

## A Table

The table below shows the first 20 rows in the dataset. How can we show the table but hide the code?

```{r}
#| label: tbl-csci-top10
#| tbl-cap: Top 20 CSCI Scores

cscidat |>
  slice_max(order_by = CSCI, n = 20) |>
  select(StationCode:COMID, E, OE, CSCI) |> 
  gt()
```
